---
title: 'Assigment 1 : Reproducible'
author: "Vinay Tyagi"
date: "Sunday, March 15, 2015"
output: html_document
---

Reading the CSV file

```{r,echo=TRUE}
activity<-read.csv("activity.csv",header=TRUE)
```

Filtering NA into another datachunk

```{r,echo=TRUE}
filter<-activity[!is.na(activity$steps),]
```

Loading Dplyr package for data manipulation
```{r,echo=TRUE}
library(dplyr)
```
Grouping daily in datachunk and calculating mean
```{r,echo=TRUE}
daily<-filter%>%group_by(date)
meanofdaily<-summarise(daily,means=mean(steps),medians=median(steps))
```
Plotting Histogram for Daily steps
```{r,echo=TRUE}
hist(x=meanofdaily$means)
```
Mean and Median for Daily steps
```{r,echo=TRUE}
meanofdaily
```
Plot Average Daily steps taken over the period
```{r,echo=TRUE}
plot(x=meanofdaily$date,y=meanofdaily$means,pch=19,type = "l")
```

Find Interval for which Maximum steps taken on an average
```{r,echo=TRUE}
maxintrvl<-daily %>% filter(steps == max(steps)) %>% select(interval,steps)
maxintrvl
```

Filling NA Values based on daily means will help us get get the full dataset
```{r,echo=TRUE}
activity2<-activity
activity2<-activity2 %>% group_by(date) %>% mutate(means = mean(steps,na.rm=TRUE))
for(i in 1:nrow(activity2))
  {
    if(is.na(activity2$steps[i]))
      {
      if(is.na(activity2$means[i]))
        {
          activity2$steps[i] <- 0
        }
      else 
        {
          activity2$steps[i] <- activity2$means[i]
        }
      
      }
  }
daily2<-activity2%>%group_by(date)
meanofdaily2<-summarise(daily2,means=mean(steps),medians=median(steps))
```
Plotting Histogram for Daily steps
```{r,echo=TRUE}
hist(x=meanofdaily2$means)
```
Mean and Median for Daily steps
```{r,echo=TRUE}
meanofdaily2
```
Plot Average Daily steps taken over the period
```{r,echo=TRUE}
plot(x=meanofdaily2$date,y=meanofdaily2$means,pch=19,type = "l")
```

Difference in weekdays and Weekend (Week days in Red and Weekend in Black)
```{r,echo=TRUE}
activity3<-activity2
activity3$weekend <- ""
for(i in 1:nrow(activity3))
{

  if((weekdays(x = as.Date(as.character(activity3[i,]$date))) %in% c("Saturday","Sunday")))
    { 
      activity3[i,]$weekend <- "weekend"
    } 
  else
    activity3[i,]$weekend <- "weekday"
}

activity3$weekend = as.factor(activity3$weekend)

activity3<-activity3 %>% group_by(interval,weekend) %>% summarise(means = mean(steps))
```

Plot for Average Interval over Weekdays and Weekends
```{r,echo=TRUE}
par(mfrow = c(2,1))
library(lattice)
xyplot(means~interval|levels(activity3$weekend) , data = activity3,xlab = "Steps")

```